On the error performance of the $A_n$ lattices

### 2011-11-15 paper.tex
minor edits to plots.
modified the plot data so that things are more visible.

%\documentclass[a4paper,10pt]{article}
%\documentclass[draftcls, onecolumn, 11pt]{IEEEtran}
\documentclass[journal]{IEEEtran}
%\documentclass[correspondence,9pt]{IEEEtran}

@@

%opening
\title{On the error performance of the $A_n$ lattices}
\author{Robby McKilliam, Ramanan Subramanian, Emanuele Viterbo}

@@

Consider a function $f : \reals^{n+1} \mapsto \reals$.  We would like to be able to solve integrals of the form
\begin{equation}\label{eq:vorfint}
\int_{\vor(A_n)} f(\xbf) d\xbf = \int_{\Qbf\vor(\ints^{n+1})} f(\xbf) d\xbf.
\end{equation}
It is not immediately clear how an integral over $\vor(A_n)$ should be performed.  Consider the following simpler integral over the hypercube $\vor(\ints^{n+1})$,
\begin{equation}\label{eq:unormalised}
\int_{\vor(\ints^{n+1})} f(\Qbf\xbf) d\xbf.
\end{equation}
This integral is not equal to~\eqref{eq:vorfint} because, although $\Qbf\xbf$ is always an element of $\vor(A_n)$, the integral is not uniform over $\vor(A_n)$.  To see this, consider some $\xbf \in \vor(\ints^{n+1})$ and let $x_{\text{max}}$ be the maximum element of $\xbf$ and $x_{\text{min}}$ be the minimum element.  Then $\xbf +  k \onebf \in \vor(\ints^{n+1})$ for those $k \in [-\nicefrac{1}{2} - x_{\text{min}}, \nicefrac{1}{2} - x_{\text{max}})$.  The length of this interval is $1 - x_{\text{max}} + x_{\text{min}}$ so the (one dimensional) volume of points in $\vor(\ints^{n+1})$ that, once projected orthogonally to $\onebf$, are equal to $\Qbf\xbf$ is given by
\[
\|\onebf\|(1 - x_{\text{max}} + x_{\text{min}}) = \sqrt{n+1}(1 - x_{\text{max}} + x_{\text{min}}).
\]
The integral~\eqref{eq:vorfint} can be obtained by normalising~\eqref{eq:unormalised} by this length, that is,
\[
\int_{\vor(A_n)} f(\xbf) d\xbf =  \int_{\vor(\ints^{n+1})} \frac{f(\Qbf\xbf)}{\sqrt{n+1}(1 - x_{\text{max}} + x_{\text{min}})}  d\xbf.
\]
The primary advantage of this integral is that the bounds are given by the hypercube $\vor(\ints^{n+1})$.

@@

Given a lattice with inradius $\rho$ and Voronoi cell having volume $V$ we define the SNR as
\[
\frac{n^2 \sigma^2 V_n}{(n+2)(\log(V_n) - \log(V) + n\log(\rho))}
\]
where $V_n$ is the volume of the $n$ dimensional hypersphere and the logarithms are base $2$.

>>>>

%\documentclass[a4paper,10pt]{article}
\documentclass[draftcls, onecolumn, 11pt]{IEEEtran}
%\documentclass[journal]{IEEEtran}
%\documentclass[correspondence,9pt]{IEEEtran}

@@

%opening
\title{On the error performance of the $A_n$ lattices}
\author{Robby McKilliam, Ramanan Subramanian, Emanuele Viterbo, I. Vaughan L. Clarkson}

@@

We would like to be able to integrate functions over the Voronoi cell of $A_n$.  The definition of $A_n$ above places it in the $n$ dimensional zero-sum plane, lying in $\reals^{n+1}$.  The Voronoi cell is a subset of the zero-sum plane and has zero $n+1$-dimensional volume.  By an appropriate change of variables it would be possible to write the Voronoi cell in an $n$-dimensional coordinate system, and then integrate.  However, we find the following approach simpler.  Given a set $S$ let $S \times \onebf$ denote the set of elements that can be writen as $x + y$ where $x \in \vor(A_n)$ and $y = k\onebf$ for some $k \in [-\nicefrac{1}{2},\nicefrac{1}{2}]$.  Consider a function $f : \reals^{n+1} \mapsto \reals$.  We would like to be able to solve integrals of the form
\begin{equation}\label{eq:vorfint}
\int_{\vor(A_n) \times \onebf} f(\Qbf\xbf) d\xbf = \int_{\Qbf\vor(\ints^{n+1}) \times \onebf} f(\Qbf\xbf) d\xbf.
\end{equation}
It is not immediately clear how an integral over $\vor(A_n) \times \onebf$ should be performed.  Consider the following simpler integral over the hypercube $\vor(\ints^{n+1})$,
\begin{equation}\label{eq:unormalised}
\int_{\vor(\ints^{n+1})} f(\Qbf\xbf) d\xbf.
\end{equation}
This integral is not equal to~\eqref{eq:vorfint} because, although $\Qbf\xbf$ is always an element of $\vor(A_n)$, the integral is not uniform over $\vor(A_n)$.  To see this, consider some $\xbf \in \vor(\ints^{n+1})$ and let $x_{\text{max}}$ be the maximum element of $\xbf$ and $x_{\text{min}}$ be the minimum element.  Then $\xbf +  k \onebf \in \vor(\ints^{n+1})$ for those $k \in [-\nicefrac{1}{2} - x_{\text{min}}, \nicefrac{1}{2} - x_{\text{max}})$.  The length of this interval is $1 - x_{\text{max}} + x_{\text{min}}$ so the (one dimensional) volume of points in $\vor(\ints^{n+1})$ that, once projected orthogonally to $\onebf$, are equal to $\Qbf\xbf$ is given by
\[
\|\onebf\|(1 - x_{\text{max}} + x_{\text{min}}) = \sqrt{n+1}(1 - x_{\text{max}} + x_{\text{min}}).
\]
The integral~\eqref{eq:vorfint} can be obtained by normalising~\eqref{eq:unormalised} by this length, that is,
\[
\int_{\vor(A_n)} f(\xbf) d\xbf =  \int_{\vor(\ints^{n+1})} \frac{f(\Qbf\xbf)}{\sqrt{n+1}(1 - x_{\text{max}} + x_{\text{min}})}  d\xbf.
\]
The primary advantage of this integral is that the bounds are given by the hypercube $\vor(\ints^{n+1})$.

@@

Given a lattice with inradius $\rho$ and Voronoi cell having volume $V$ we define the SNR as
\[
\frac{V_n}{\sigma^2(n+2)(\log(V_n) - \log(V) + n\log(\rho))}
\]
where $V_n$ is the volume of the $n$ dimensional hypersphere and the logarithms are base $2$.
